calerror

### 2024-01-30 simCalibration.Rmd
sims

results_all <- rbindlist(lapply(1:100, function(iter) {
  try({
  results <- rbindlist(lapply(c(1, 1.5, 2, 2.5, 3, 4, 5), get_widths_cal) )
  results$iter <- iter
  })
  return(results)
}))

>>>>

results_all <- rbindlist(lapply(1:1000, function(iter) {
  try({
  results <- rbindlist(lapply(c(1,1.25, 1.5, 1.75, 2,2.25,  2.5,2.75, 3, 3.5, 4, 4.5, 5), get_widths_cal) )
  results$iter <- iter
  })
  return(results)
}))
